```{r}
library(readr)
library(dplyr)
library(lubridate)

source("../feature_creation.R")
```
####
Make features for mainnet v2
####
```{r}
mainnetV2Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Mainnet/transactionsNew.rds")
mainnetV2_user <- add_coin_type(mainnetV2Original)
mainnetV2_user <- add_user_object_modes(mainnetV2_user)
mainnetV2_user <- add_cumulative_user_history(mainnetV2_user)
mainnetV2_user <- add_windowed_user_history(mainnetV2_user)
# Write the standardized features to disk:
saveRDS(mainnetV2_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Mainnet/transactions_user.rds")
```
```{r}
mainnetV2_user_time <- create_time_features(mainnetV2_user)
# Write the standardized features to disk:
saveRDS(mainnetV2_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Mainnet/transactions_user_time.rds")
```

```{r}
mainnetV2_user_market_time <- add_windowed_market_history(mainnetV2_user_time)
saveRDS(mainnetV2_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Mainnet/transactions_user_market_time.rds")
```


####
Make features for avalanche v2
####
```{r}
avalancheV2Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Avalanche/transactions.rds")
avalancheV2_user <- add_coin_type(avalancheV2Original)
avalancheV2_user <- add_user_object_modes(avalancheV2_user)
avalancheV2_user <- add_cumulative_user_history(avalancheV2_user)
avalancheV2_user <- add_windowed_user_history(avalancheV2_user)
# Write the standardized features to disk:
saveRDS(avalancheV2_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Avalanche/transactions_user.rds")
```
```{r}
avalancheV2_user_time <- create_time_features(avalancheV2_user)
# Write the standardized features to disk:
saveRDS(avalancheV2_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Avalanche/transactions_user_time.rds")
```

```{r}
avalancheV2_user_market_time <- add_windowed_market_history(avalancheV2_user_time)
saveRDS(avalancheV2_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Avalanche/transactions_user_market_time.rds")
```
####
Make the same sets of features for polygon v2:
####
```{r}
polygonV2Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Polygon/transactions.rds")
polygonV2_user <- add_coin_type(polygonV2Original)
polygonV2_user <- add_user_object_modes(polygonV2_user)
polygonV2_user <- add_cumulative_user_history(polygonV2_user)
polygonV2_user <- add_windowed_user_history(polygonV2_user)
# Write the standardized features to disk:
saveRDS(polygonV2_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Polygon/transactions_user.rds")
```
```{r}
polygonV2_user_time <- create_time_features(polygonV2_user)
# Write the standardized features to disk:
saveRDS(polygonV2_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Polygon/transactions_user_time.rds")
```

```{r}
polygonV2_user_market_time <- add_windowed_market_history(polygonV2_user_time)
saveRDS(polygonV2_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V2/Polygon/transactions_user_market_time.rds")
```
####
Make the same sets of features for polygon v3:
####
```{r}
polygonV3Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Polygon/transactions.rds")
polygonV3_user <- add_coin_type(polygonV3Original)
polygonV3_user <- add_user_object_modes(polygonV3_user)
polygonV3_user <- add_cumulative_user_history(polygonV3_user)
polygonV3_user <- add_windowed_user_history(polygonV3_user)
# Write the standardized features to disk:
saveRDS(polygonV3_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Polygon/transactions_user.rds")
```
```{r}
polygonV3_user_time <- create_time_features(polygonV3_user)
# Write the standardized features to disk:
saveRDS(polygonV3_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Polygon/transactions_user_time.rds")
```

```{r}
polygonV3_user_market_time <- add_windowed_market_history(polygonV3_user_time)
saveRDS(polygonV3_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Polygon/transactions_user_market_time.rds")
```
####
Make the same sets of features for harmony v3:
####
```{r}
harmonyV3Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Harmony/transactions.rds")
harmonyV3_user <- add_coin_type(harmonyV3Original)
harmonyV3_user <- add_user_object_modes(harmonyV3_user)
harmonyV3_user <- add_cumulative_user_history(harmonyV3_user)
harmonyV3_user <- add_windowed_user_history(harmonyV3_user)
# Write the standardized features to disk:
saveRDS(harmonyV3_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Harmony/transactions_user.rds")
```
```{r}
harmonyV3_user_time <- create_time_features(harmonyV3_user)
# Write the standardized features to disk:
saveRDS(harmonyV3_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Harmony/transactions_user_time.rds")
```

```{r}
harmonyV3_user_market_time <- add_windowed_market_history(harmonyV3_user_time)
saveRDS(harmonyV3_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Harmony/transactions_user_market_time.rds")
```

####
Make the same sets of features for fantom v3:
####
```{r}
fantomV3Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Fantom/transactions.rds")
fantomV3_user <- add_coin_type(fantomV3Original)
fantomV3_user <- add_user_object_modes(fantomV3_user)
fantomV3_user <- add_cumulative_user_history(fantomV3_user)
fantomV3_user <- add_windowed_user_history(fantomV3_user)
# Write the standardized features to disk:
saveRDS(fantomV3_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Fantom/transactions_user.rds")
```
```{r}
fantomV3_user_time <- create_time_features(fantomV3_user)
# Write the standardized features to disk:
saveRDS(fantomV3_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Fantom/transactions_user_time.rds")
```

```{r}
fantomV3_user_market_time <- add_windowed_market_history(fantomV3_user_time)
saveRDS(fantomV3_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Fantom/transactions_user_market_time.rds")
```
####
Make the same sets of features for optimism v3:
####
```{r}
optimismV3Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Optimism/transactions.rds")
optimismV3_user <- add_coin_type(optimismV3Original)
optimismV3_user <- add_user_object_modes(optimismV3_user)
optimismV3_user <- add_cumulative_user_history(optimismV3_user)
optimismV3_user <- add_windowed_user_history(optimismV3_user)
# Write the standardized features to disk:
saveRDS(optimismV3_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Optimism/transactions_user.rds")
```
```{r}
optimismV3_user_time <- create_time_features(optimismV3_user)
# Write the standardized features to disk:
saveRDS(optimismV3_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Optimism/transactions_user_time.rds")
```

```{r}
optimismV3_user_market_time <- add_windowed_market_history(optimismV3_user_time)
saveRDS(optimismV3_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Optimism/transactions_user_market_time.rds")
```

####
Make the same sets of features for avalanche v3:
####
```{r}
avalancheV3Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Avalanche/transactions.rds")
avalancheV3_user <- add_coin_type(avalancheV3Original)
avalancheV3_user <- add_user_object_modes(avalancheV3_user)
avalancheV3_user <- add_cumulative_user_history(avalancheV3_user)
avalancheV3_user <- add_windowed_user_history(avalancheV3_user)
# Write the standardized features to disk:
saveRDS(avalancheV3_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Avalanche/transactions_user.rds")
```
```{r}
avalancheV3_user_time <- create_time_features(avalancheV3_user)
# Write the standardized features to disk:
saveRDS(avalancheV3_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Avalanche/transactions_user_time.rds")
```

```{r}
avalancheV3_user_market_time <- add_windowed_market_history(avalancheV3_user_time)
saveRDS(avalancheV3_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Avalanche/transactions_user_market_time.rds")
```


####
Make the same sets of features for arbitrum v3:
####
```{r}
arbitrumV3Original <- read_rds("/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Arbitrum/transactions.rds")
arbitrumV3_user <- add_coin_type(arbitrumV3Original)
arbitrumV3_user <- add_user_object_modes(arbitrumV3_user)
arbitrumV3_user <- add_cumulative_user_history(arbitrumV3_user)
arbitrumV3_user <- add_windowed_user_history(arbitrumV3_user)
# Write the standardized features to disk:
saveRDS(arbitrumV3_user, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Arbitrum/transactions_user.rds")
```
```{r}
arbitrumV3_user_time <- create_time_features(arbitrumV3_user)
# Write the standardized features to disk:
saveRDS(arbitrumV3_user_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Arbitrum/transactions_user_time.rds")
```

```{r}
arbitrumV3_user_market_time <- add_windowed_market_history(arbitrumV3_user_time)
saveRDS(arbitrumV3_user_market_time, file="/data/IDEA_DeFi_Research/Data/Lending_Protocols/Aave/V3/Arbitrum/transactions_user_market_time.rds")
```
```{r}

```