
```{r}
save_pheatmap_png <- function(x, filename, width=1200, height=1000, res = 150) {
  png(filename, width = width, height = height, res = res)
  grid::grid.newpage()
  grid::grid.draw(x$gtable)
  dev.off()
}
```
Load necessary libraries:
```{r}
library(pheatmap)
library(dplyr)
library(xtable)
library(readr)
library(tidyr)
library(tibble)
library(ggpubr)
```

```{r}
pubFontSize = 18
pValSize = 8
pubWidth = 8
pubHeight = 6
pubColorScheme = "Set1"
```


# Read in the prediction results and rename columns to just be model names:
```{r}
benchmark_results <- read_csv("../Results/Survival_Prediction/originalBenchmark/final_results.csv") %>%
  select(-GBM, -DeepHit, -DeepSurv) %>%
  mutate(features = "benchmark") %>%
  mutate(outcomeEvent = case_when(outcomeEvent == "account liquidated" ~ "liquidated",
                                  TRUE ~ outcomeEvent)) %>%
  mutate(dataset = paste0(indexEvent, "-", outcomeEvent)) %>%
  select(-indexEvent, -outcomeEvent)
raw_results <- read_rds("../Results/Survival_Prediction/raw_seqLen10/results.rds") %>%
  mutate(features = "raw") %>%
  mutate(outcomeEvent = case_when(outcomeEvent == "Account Liquidated" ~ "liquidated",
                                  TRUE ~ tolower(outcomeEvent))) %>%
  mutate(dataset = paste0(tolower(indexEvent), "-", outcomeEvent)) %>%
  select(-indexEvent, -outcomeEvent) %>%
  mutate(model = str_remove(model, "_.*$")) %>%
  pivot_wider(names_from = "model",
              values_from = "c_index")
  
ltm_results <- read_rds("../Results/Survival_Prediction/ltm_seqLen10/results.rds") %>%
  mutate(features = "LTM") %>%
  mutate(outcomeEvent = case_when(outcomeEvent == "Account Liquidated" ~ "liquidated",
                                  TRUE ~ tolower(outcomeEvent))) %>%
  mutate(dataset = paste0(tolower(indexEvent), "-", outcomeEvent)) %>%
  select(-indexEvent, -outcomeEvent) %>%
  mutate(model = str_remove(model, "_.*$")) %>%
  pivot_wider(names_from = "model",
              values_from = "c_index")
```

```{r}
all_results <- bind_rows(benchmark_results, raw_results, ltm_results)

results_long <- all_results %>%
  pivot_longer(
    cols = -c(dataset, features),
    names_to = "model",
    values_to = "c_index"
  )
```

```{r}
library(ggplot2)
library(RColorBrewer)

ggplot(results_long, aes(x = features, y = dataset, fill = c_index)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(colors = colorRampPalette(rev(brewer.pal(9, "RdYlBu")))(100)) +  # you can tune colors
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  # rotate model names
  facet_wrap(~ model) +
  labs(
    title = "Model Performance Across Feature Sets",
    x = "Model",
    y = "Dataset",
    fill = "C-index"
  ) + 
  geom_text(aes(label = sprintf("%.2f", c_index)), size = 3)
```
Now do all the same things for the classification results:
```{r}
benchmark_results <- read_csv("../Results/Survival_Classification/originalBenchmark/auc_score.csv") %>%
  select(-DeepHit, -DeepLearningClassifier) %>%
  mutate(features = "benchmark") %>%
  rename(dataset = auc_score) %>%
  mutate(dataset = str_replace(dataset, "account liquidated", "liquidated")) %>%
  rename(LogReg = Logistic.Regression,
         DecisionTree = Decision.Tree,
         ElasticNet = Elastic.Net)

raw_results <- read_rds("../Results/Survival_Classification/raw_seqLen10/results.rds") %>%
  mutate(features = "raw") %>%
  mutate(outcomeEvent = case_when(outcomeEvent == "Account Liquidated" ~ "liquidated",
                                  TRUE ~ tolower(outcomeEvent))) %>%
  mutate(dataset = paste0(tolower(indexEvent), " + ", outcomeEvent)) %>%
  select(-indexEvent, -outcomeEvent, -smote) %>%
  mutate(model = str_remove(model, "_.*$")) %>%
  pivot_wider(names_from = "model",
              values_from = "auc")
  
ltm_results <- read_rds("../Results/Survival_Classification/ltm_seqLen10/lr_dt_en_results_ltm_small.rds") %>%
  bind_rows(read_rds("../Results/Survival_Classification/ltm_seqLen10/resultsXGB_ltm_small.rds")) %>%
  mutate(features = "LTM") %>%
  mutate(outcomeEvent = case_when(outcomeEvent == "Account Liquidated" ~ "liquidated",
                                  TRUE ~ tolower(outcomeEvent))) %>%
  mutate(dataset = paste0(tolower(indexEvent), " + ", outcomeEvent)) %>%
  select(-indexEvent, -outcomeEvent, -smote, -f1) %>%
  mutate(auc = as.numeric(auc)) %>%
  mutate(model = str_remove(model, "_.*$")) %>%
  pivot_wider(names_from = "model",
              values_from = "auc") 
```


```{r}
all_results <- bind_rows(benchmark_results, raw_results, ltm_results)
all_results_1 <- all_results %>%
  select(-ElasticNet, -XGBoost)
all_results_2 <- all_results %>%
  select(-LogReg, -DecisionTree)

results_long_1 <- all_results_1 %>%
  pivot_longer(
    cols = -c(dataset, features),
    names_to = "model",
    values_to = "auc"
  )

results_long_2 <- all_results_2 %>%
  pivot_longer(
    cols = -c(dataset, features),
    names_to = "model",
    values_to = "auc"
  )

```



```{r}
library(ggplot2)
library(RColorBrewer)

ggplot(results_long_1, aes(x = features, y = dataset, fill = auc)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(colors = colorRampPalette(rev(brewer.pal(9, "RdYlBu")))(100)) +  # you can tune colors
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  # rotate model names
  facet_wrap(~ model) +
  labs(
    title = "Model Performance Across Feature Sets",
    x = "Model",
    y = "Dataset",
    fill = "AUC"
  ) + 
  geom_text(aes(label = sprintf("%.2f", auc)), size = 3)
```

```{r}
library(ggplot2)
library(RColorBrewer)

ggplot(results_long_2, aes(x = features, y = dataset, fill = auc)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(colors = colorRampPalette(rev(brewer.pal(9, "RdYlBu")))(100)) +  # you can tune colors
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  # rotate model names
  facet_wrap(~ model) +
  labs(
    title = "Model Performance Across Feature Sets",
    x = "Model",
    y = "Dataset",
    fill = "AUC"
  ) + 
  geom_text(aes(label = sprintf("%.2f", auc)), size = 3)
```

Rename the auc_score column as Dataset, convert the '+' to '-', and shorten "account liquidated" to "liquidated"
```{r}
classification_results <- classification_results %>%
  rename(Dataset = auc_score) %>%
  rename(LogReg = Logistic.Regression)

# Step 1: Replace " + " with "-"
classification_results$Dataset <- gsub(" \\+ ", "-", classification_results$Dataset)


# Step 2: Replace "account liquidated" with "liquidated"
classification_results$Dataset <- gsub("account liquidated", "liquidated", classification_results$Dataset, fixed = TRUE)
```

Rearrange the rows and columns according to their Mean Borda Rank:
```{r}
# Use the Dataset column as rownames:
classification_results <- classification_results %>%
  column_to_rownames(var = "Dataset")

# Also, rename "DeepLearningClassifier" as Neural Net:
classification_results <- classification_results %>%
  rename(NeuralNet = DeepLearningClassifier)

# Calculate the means of the columns (mean concordance index for each model):
col_means <- colMeans(classification_results)
classification_results <- bind_rows(classification_results, col_means) 
rownames(classification_results)[rownames(classification_results) == "...17"] <- "Mean AUC"

# Calculate the Borda ranks for the columns:
col_ranks <- data.frame(classification_results) %>%
         rowwise() %>% 
         do(data.frame(t(rank(-unlist(.)))))
# This is a bit janky, but I know there are only 16 datasets, 
# so just keep the top 16 rows after the col_ranks have been computed:
col_ranks <- col_ranks %>%
  head(16)

mean_col_ranks <- colMeans(col_ranks)
classification_results<- bind_rows(classification_results, mean_col_ranks)
rownames(classification_results)[rownames(classification_results) == "...18"] <- "Mean Borda Rank"
classification_results[18, ] = classification_results[18, ] / 6

# Order column names based on their means (ascending)
ordered_cols <- classification_results[, order(as.numeric(classification_results["Mean Borda Rank", ]))]

# Set up the dataframe for annotating heatmap columns based on Borda Rank
annot_cols <- as.numeric(ordered_cols["Mean Borda Rank", ])
names(annot_cols) <- colnames(ordered_cols)
annot_cols <- data.frame(`Mean Borda Rank` = annot_cols)

classification_results_for_heatmap <- ordered_cols[1:16, ]

# Next, let's order the columns by Borda rank by transposing the matrix and doing the same thing as above:
classification_results_transposed <- data.frame(t(classification_results_for_heatmap)) 
row_means <- colMeans(classification_results_transposed)
classification_results_transposed <- bind_rows(classification_results_transposed, row_means)
rownames(classification_results_transposed)[rownames(classification_results_transposed) == "...7"] <- "Mean AUC"

row_ranks <- data.frame(classification_results_transposed) %>%
  rowwise() %>%
  do(data.frame(t(rank(-unlist(.)))))

row_ranks <- row_ranks %>%
  head(6)

mean_row_ranks <- colMeans(row_ranks)
classification_results_transposed <- bind_rows(classification_results_transposed, mean_row_ranks)
rownames(classification_results_transposed)[rownames(classification_results_transposed) == "...8"] <- "Mean Borda Rank"
classification_results_transposed[8, ] = classification_results_transposed[8, ] / 16

annot_rows <- as.numeric(classification_results_transposed["Mean Borda Rank", ])
names(annot_rows) <- colnames(classification_results_transposed)
annot_rows <- data.frame(`Mean Borda Rank` = annot_rows)

rownames(annot_rows) <- rownames(classification_results_for_heatmap)

final_row_order <- annot_rows %>%
  arrange(Mean.Borda.Rank) %>%
  rownames()

classification_results_for_heatmap <- classification_results_for_heatmap[final_row_order,]


classification_results_heatmap <- pheatmap(as.matrix(classification_results_for_heatmap), scale='none',
                                           breaks = myBreaks,
         angle_col = 45,
         main = "Classification AUC Values", 
         cluster_cols = FALSE, cluster_rows = FALSE,
         display_numbers = TRUE,
         annotation_col = annot_cols,
         annotation_row = annot_rows,
         annotation_names_row = FALSE,
         annotation_names_col = FALSE,
         width = 1280,
         height = 720
         )

```
With the heatmap created and looking good, let's save it to a PDF for publication-readiness:
```{r}
image=ggpubr::ggpar(classification_results_heatmap,
              font.legend = list(size = pubFontSize),
              font.xtickslab = list(size = pubFontSize),
              font.ytickslab = list(size = pubFontSize),
              font.x = list(size = pubFontSize),
              font.y = list(size = pubFontSize),
              font.subtitle = list(size = pubFontSize),
              palette = pubColorScheme)
ggsave(file="classificationResults.pdf", plot=image, width=pubWidth, height=pubHeight)
```
```{r}
xtable(classification_results, digits=c(0, 3, 3, 3, 3, 3, 3))
```

